Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
grant numbers straightened out

[grant numbers for the DARPA/GALE grants here]

Matthew Snover is supported under the GALE Program, DARPA/IPTO
Contract No. HR0011-06-C-0022.

>>>>

This material is based upon work supported by the National Science
Foundation under Grant No. 0741585 and the Defense Advanced Research
Projects Agency under Contract Nos. HR0011-06-C-0022 and HR0011-06-C-0023.

% Re: DARPA contract numbers
% -0022 is Matt's [Agile] grant.
% -0023 is Mari & Jeremy's [Nightingale] grant

Any opinions, findings, and conclusions or recommendations expressed
in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation or the Defense
Advanced Research Projects Agency.
